The Impact of the 2022-23 NBA Rule Change

### 2024-04-21 paper/paper.qmd
Update model

library(tidyverse)
library(knitr)
library(dplyr)
library(cowplot)

@@

# Create a data frame containing the model summary information
model_summary <- tibble(
  "Variable" = c("(Intercept)", "field_goal_percentage", "three_points_percentage", "free_throw_percentage"),
  "Estimate" = c(-4628, 7399, 7410, -1640),
  "Std. Error" = c(2004, 1994, 3740, 1417),
  "t value" = c(-2.310, 3.712, 1.981, -1.158),
  "Pr(>|t|)" = c(0.06028, 0.00995, 0.09485, 0.29093)
)

# Convert the data frame to a modelsummary table
summary_table <- modelsummary(model_summary)

summary_table

>>>>

library(tidyverse)
library(knitr)
library(dplyr)
library(cowplot)
library(modelsummary)
library(kableExtra)

@@

# Generate a summary table with numerical values formatted to 2 decimal places
model_table <- modelsummary(
  list("2022-23 Season" = model2023),
  fmt = 2
)

model_table
```
